Test of Adaptable User Interfaces

### 2015-07-08 paper.tex

% =============================================================================
\section{Case Study}
% =============================================================================
TODO

>>>>

% =============================================================================
\section{Case Study}
The case study used in this work is a prototype for a smart home energy management system. This decision is based on the fact that it is a modern concept, little explored in the domain of this research and whose UIs can be adapted to several contexts. A smart home may be defined as a well-designed structure with sufficient access to assets, communication, controls, data, and information technologies for enhancing the occupants' quality of life through comfort, convenience, reduced costs and increased connectivity~\cite{smart-home-harper}. A smart home energy management system is an energy management system applied to smart homes. It allows users to control and monitor the energy consumption in a residence from different devices.

It is a prototype because we have developed only the UIs of the system for four versions, three for web environment and one as a mobile application. The data of the system are predetermined. All versions have the same features, except for two web versions that have an additional feature. The differences between the versions are visual. In the case of the mobile application, the UI is adapted to a mobile device, which contains a smaller screen and its own platform for UI development. In the case of the web versions, the UIs have also been developed to this context, using web UI technologies. But the differences between the three web versions are changes in the navigation and UI components. In this paper, we focus on the following features of the prototype:

\begin{enumerate}

\item \textbf{Goal}: the user can check information about the general energy consumption per month. Having access to the goal and consumption in kWh for the chosen month.

\item \textbf{Filter}: the user has access to a list of all his or her objects in the house, having the possibility to filter this list per room. An object means any component that can be controlled and whose energy consumption can be registered, such as lights and electronic devices.

\item \textbf{Comparator}: the user can choose two objects and compare, side by side, their energy consumption charts. This feature is present in only two of the web versions.

\end{enumerate}
